Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/wg_main_user_community.tex
added plans

\subsubsection{Plans}
\todo{short text here - not bullets}

>>>>

\subsubsection{Plans}
%\todo{short text here - not bullets}

The most important next steps is a ``Best Practice'' document, which would describe what successful projects with engaged communities look like, how to replicate this type of project, and look at end-of-life on a community project. Inputs to this document would include a software community survey of high functioning communities such as R Open Science, Python SciPy, OPeNDAP, and Unidata, with analysis of factors that feed into their success. Also references lik the "Art of Community" could be adapted and summarized for the science software community.

Another next step would be increasing recognition of need for science software projects to focus on building and supporting their user community. Good Software Engineering practices are not enough, and popular training like Software Carpentry does not currently address this issue head on.
